Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-06 paper/ms.tex
update RM amplitude for limb darkening

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta
    T=4.7$, $2.3''$ west) is detected in the autocorrelation function,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:}
    Radial velocity (RV) measurements, with best-fit instrument
    offsets and jitter terms included.  The expected scatter from
    starspots based on $v\sin i$ and the photometric modulation
    amplitude is of order 300m$\,$s$^{-1}$.  {\it Bottom:} RV
    measurements phased to the orbital ephemeris of \pn.  The planet
    is not detected.  The black line shows a circular Keplerian orbit
    representing the $3\sigma$ upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{winn_exoplanet_2010}
\begin{align}
  \Delta V_{\rm RM} \approx \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 21\,{\rm m\,s}^{-1},
\end{align}
where we have assumed stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}, and for
calculation purposes we assumed $b=0.95$.  This is challenging, but
for a 1.9$\,$hr transit of a $V=10.6$ star, a detection could be achieved
with modern spectrographs.  The next viable total transit windows from
Chile occur in January and February of 2021; there are also a few
visible per season from other southern locations.

>>>>

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.46\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta
    T=4.7$, $2.3''$ west) is detected in the autocorrelation function,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:}
    Radial velocity (RV) measurements, with best-fit instrument
    offsets and jitter terms included.  The expected scatter from
    starspots based on $v\sin i$ and the photometric modulation
    amplitude is of order 300m$\,$s$^{-1}$.  {\it Bottom:} RV
    measurements phased to the orbital ephemeris of \pn.  The planet
    is not detected.  The black line shows a circular Keplerian orbit
    representing the $3\sigma$ upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.
